Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD

### 2019-10-12 paper/cvpr2020/sections/hardware.tex
pass over simulated results section
Removed whitespace from comparison figure.

\begin{figure}[H]
  \includegraphics[width=\linewidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

@@

As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW. The SPAD records temporal histograms with 65536 bins, each corresponding to a time window of 4~ps. SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels. The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm that only uses the single histogram of the diffused SPAD and compare it with ground truth. Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.

@@

Using this prototype, we captured a number of scenes as shown in Figure~\ref{fig:results_captured} and in the supplement. We downsample the reference RGB image to a resolution of $XX \times XX$~px and directly feed into a monocular depth estimation algorithm. In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested. Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement. The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).

>>>>

\begin{figure}[t!]
	\centering
  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

@@

As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW. The SPAD records temporal histograms with 16384 bins, each corresponding to a time window of 16~ps. SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm. A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels. The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene. This allows us to validate the accuracy of the proposed histogram matching algorithm that only uses the single histogram of the diffused SPAD and compare it with ground truth. Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.

@@

Using this prototype, we captured a number of scenes as shown in
Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
to have dimensions that are multiples of 32. For DORN only, we further
downsample the image to a resolution of $353 \times 257$. We then feed this RGB
image into the monocular depth estimation algorithm. In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested. Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement. The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).
